---
title: "Profile Viewer"
output:
  html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rgl)
library(knitr)
knit_hooks$set(webgl = hook_webgl)
```

## Instructions

* First, go to this webpage: https://get.webgl.org/ to make sure you have the extension enabled to view the 3D figures. 
* Scroll to zoom in/out; click and drag to rotate. 
* Points are numbered and color-coded:
  + Blue = surveyed as profile
  + Red = surveyed as scarp midpoint
  + Yellow = surveyed as scarp face (on straight-line profiles)
* In the excel file, notate the first and last point you choose for each uphill and downhill segment, as well as any points within that range you'd like to exclude.
* For the straight-line profiles, notate if you would like to choose a different midpoint than the one I chose in the field. The midpoint should be the steepest part of the scarp face (the point of inflection) - where the fault is most likely to intersect the ground surface.

## Site 2 


```{r CL, webgl=TRUE, echo=FALSE,class.source="site2"}
survey <- read.csv(file="CL.csv", header=TRUE, sep=",") # prepared survey csv or txt file. make sure you are working in the same directory as your profiles
profile1 = "CL"

profile_plot <- function(survey, profile1) {
  init_midpt = subset(survey, survey[, 5] == "M") # currently have to choose same midpoint for each person
  
  survey$Easting<-(survey$Easting - init_midpt$Easting)
  survey$Northing<-(survey$Northing - init_midpt$Northing)
  survey$HAE<-(survey$HAE - init_midpt$HAE)
  
  #redefine midpoint as origin
  midpt = subset(survey,survey[,5] =="M")
  
  # define sections of the profile separated by fault strands
  profile=subset(survey, survey[,5] == "U") # uphill section
  scarp=subset(survey, survey[,5] == "L") # downhill section
  
  #plot the profile in 3D space, with option to click and drag to spin the plot
  plot3d(x = profile$Easting, y = profile$Northing, z = profile$HAE,aspect="iso",
         xlab="Easting (m)",ylab="Northing (m)",zlab="Elevation (m)",col="blue",main=profile1)
  #aspect="iso" means isometric - E/N/Z are all to scale - no vertical exaggeration
  points3d(x=midpt$Easting,y=midpt$Northing,z=midpt$HAE,col="red")
  points3d(x=scarp$Easting,y=scarp$Northing,z=scarp$HAE,col="yellow")
  text3d(x=survey$Easting,y=survey$Northing,z=survey$HAE,survey$Point,pos=4,offset=0.5,cex=0.6)
}
profile_plot(survey,profile1)
bg3d("lightgray")
```
**CL** Straight-line profile.

```{r JM_1, webgl=TRUE, echo=FALSE}
survey <- read.csv(file="JM_1.csv", header=TRUE, sep=",") # prepared survey csv or txt file
profile1 = "JM_1"
profile_plot(survey,profile1)
```
**JM 1** Straight-line profile.

```{r JM_2_TT, webgl=TRUE, echo=FALSE}
survey <- read.csv(file="JM_2_TT.csv", header=TRUE, sep=",") # prepared survey csv or txt file
profile1 = "JM_2_TT"
profile_plot(survey,profile1)
```
**JM 2/TT** Straight-line profile.

```{r KP, webgl=TRUE, echo=FALSE}
survey <- read.csv(file="KP.csv", header=TRUE, sep=",") # prepared survey csv or txt file
profile1 = "KP"
profile_plot(survey,profile1)
```
**KP** Straight-line profile.

```{r KPTH, webgl=TRUE, echo=FALSE}
survey <- read.csv(file="KPTH.csv", header=TRUE, sep=",") # prepared survey csv or txt file
profile1 = "KPTH"
profile_plot(survey,profile1)
```
**KPTH** Offset active channel.

```{r TH1, webgl=TRUE, echo=FALSE}
survey <- read.csv(file="TH1.csv", header=TRUE, sep=",") # prepared survey csv or txt file
profile1 = "TH1"
profile_plot(survey,profile1)
```
**TH 1** Offset abandoned channel.

```{r TH2, webgl=TRUE, echo=FALSE}
survey <- read.csv(file="TH2.csv", header=TRUE, sep=",") # prepared survey csv or txt file
profile1 = "TH2"
profile_plot(survey,profile1)
```
**TH 2** Offset abandoned channel.

```{r FWS, webgl=TRUE, echo=FALSE}
survey <- read.csv(file="FWS.csv", header=TRUE, sep=",") # prepared survey csv or txt file
profile1 = "FWS"
profile_plot(survey,profile1)
```
**FWS** Straight-line profile.

##repeat these chunks as many times as needed to plot all of your profiles.